### 2021-03-30 exploratory/2021/plots.Rmd
Update w/ new opticlust; virtually the same

theme_set(theme_classic())
color_palette <- RColorBrewer::brewer.pal(4, "Dark2")
dataset_colors <- c(
  human = color_palette[[3]],
  marine = color_palette[[1]],
  mouse = color_palette[[4]],
  soil = color_palette[[2]]
)
tri_colors <-  c("darkorange","darkorchid","cyan4") # https://allisonhorst.github.io/palmerpenguins/articles/intro.html
mutate_perf <- function(dat) {
  dat %>% 
    mutate(mem_mb = max_rss,
           mem_gb = mem_mb / 1024) %>% 
    rename(sec = s,
           num_otus = sobs)
}
```

>>>>

theme_set(theme_classic())
color_palette <- RColorBrewer::brewer.pal(4, "Dark2")
dataset_colors <- c(
  human = color_palette[[3]],
  marine = color_palette[[1]],
  mouse = color_palette[[4]],
  soil = color_palette[[2]]
)
tri_colors <-  c("darkorange","darkorchid","cyan4") # https://allisonhorst.github.io/palmerpenguins/articles/intro.html
mutate_perf <- function(dat) {
  dat %>% 
    mutate(mem_mb = max_rss,
           mem_gb = mem_mb / 1024) %>% 
    rename(sec = s)
}
```
